A reproducible journal article with RMarkdown&#58; A  building science template with examples for beginners based on the Elsevier journal format

### 2019-02-15 Paper/Manuscript.Rmd
Add two more software citations

-   base R - @base
-   ggpmisc - @ggpmisc
-   grateful  - @grateful
-   gt - @gt
-   here  - @here
-   knitr - @knitr
-   tidyverse -  @tidyverse
-   rticles - @rticles

```{r include = FALSE}
pkgs <- c("here", "knitr", "ggpmisc", "gt", "grateful", "base", "rticles")
cites <- grateful::get_citations(pkgs, filename = "pkg-refs.bib", out.dir =  here("/Paper/SupplementaryMaterial/Software_citations") )
```

>>>>

-   base R - @base
-   ggpmisc - @ggpmisc
-   grateful  - @grateful
-   gt - @gt
-   here  - @here
-   knitr - @knitr
-   tidyverse -  @tidyverse
-   rticles - @rticles
-   bookdown - @bookdown
-   rmarkdown - @rmarkdown

```{r include = FALSE}
pkgs <- c("here", "knitr", "ggpmisc", "gt", "grateful", "base", "rticles", "bookdown", "rmarkdown", "tidyverse")
cites <- grateful::get_citations(pkgs, filename = "pkg-refs.bib", out.dir =  here("/Paper/SupplementaryMaterial/Software_citations") )
```
